Measurement and Probability in Fuzzy Quantum Theories

### 2017-07-08 prop_iop.tex
prop_letter.pptx "Recover QRVPM and CIVPM as a special case" Updating...

>>>>

Lemma~\ref{lemma:QIVPM2QCM} may be extended in another trivial way.

\begin{lemma}If every interval in $\mathscr{I}$ is a singleton set,
given a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, then
$\mu:\events\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
is a quantum probability measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have
\begin{eqnarray*}
 &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\\
 & \Rightarrow & \left\{ \mu\left(\mathbb{1}-P\right)\right\} =\left[1,1\right]-\left\{ \mu\left(P\right)\right\} =\left\{ 1-\mu\left(P\right)\right\} \\
 & \Rightarrow & \mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)\,.
\end{eqnarray*}
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
have
\begin{eqnarray*}
 &  & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
 & \Rightarrow & \left\{ \mu\left(P_{0}+P_{1}\right)\right\} \subseteq\left\{ \mu\left(P_{0}\right)\right\} +\left\{ \mu\left(P_{1}\right)\right\} =\left\{ \mu\left(P_{0}\right)+\mu\left(P_{1}\right)\right\} \\
 & \Rightarrow & \mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.
\end{eqnarray*}
\end{itemize}
\end{proof}

Together with example~\ref{ex:regular-pair}, we know QIVPMs with
$\mathscr{I}_{\infty}$ is one-to-one correspondence to quantum real-valued
probability measures.
